---
title: 'Table of datasets used in this app'
output: html_document
---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, include=FALSE}
library(gt)
DOIs_metadata <-  readr::read_csv(here::here("data/DOIs_enriched.csv")) %>% 
    # dplyr::select(c("identifier","title","DOI","Filename")) %>% dplyr::rename("Identifier"=identifier,"Title"=title) %>% 
    dplyr::select(c("Rmd_badge","URL","Filename","title","Citation")) %>% 
    # dplyr::mutate(Citation= RefManageR::Cite(RefManageR::GetBibEntryWithDOI(URL), .opts = list(style = "text", bib.style = "authoryear")))  %>% 
    dplyr::rename("DOI-Link"=Rmd_badge,"Title"=title, Url= URL) 
# zenodo_DOI_template="doc/zenodo.111222333444.svg"
# con <- file(here::here(zenodo_DOI_template),"r")
# lines <- readLines(con)
# close(con)
# new_lines <- gsub(pattern = "",replacement = record_id,lines)
# gsub(pattern_session_id,paste0("10.5281/zenodo.111222333444",DOI),DOI)
# zenodo_DOI_filename <- gsub(pattern = "111222333444",replacement = record_id,zenodo_DOI_template)
# fileConn<-file(here::here("doc/zenodo.111222333444.svg"))
# writeLines(new_lines, fileConn)
# close(fileConn)
# system(paste0("qgis --project ",  paste0(session_directory,"/METADATA/QGIS_project_",session_id,".qgs")," --snapshot a_raw_drone_data_map_preview.jpg --width 3200 --height 2400"))
    
```

<!-- ## table of thumbnails -->

<div id="modal" name="modal" style="border:solid">


# Data

The default datasets used by this app have been assigned DOIs on Zenodo :



```{r  echo=F ,results='asis' }
DOIs_metadata |> 
    gt() |> 
    tab_header(
      title = "Undelrying datasets",
      subtitle = "Zenodo DOIs"
    )  |> 
    fmt_markdown(columns = DOI-Link) |> 
    fmt_markdown(columns = Citation) |> 
    fmt_url(columns = Url)  |> 
    tab_style(
      style = cell_borders(
        # sides = c("t", "l"),
        color = "black",
        weight = px(3)
      ),
      locations = cells_body()
    ) 
# |>
#   gtExtras::gt_img_rows(columns = Rmd_badge, height = 25)|>
#   cols_merge(
#     columns = c(Rmd_badge, Url), pattern = "{1} {2}"
#   ) 
# |> 
#   gtExtras::gt_hyperlink(text =svg_badge, url = "https://rdrr.io/github/jthomasmock/gtExtras/man/gt_hyperlink.html")
  # gtExtras::gt_hyperlink(text =svg_badge, url = "https://rdrr.io/github/jthomasmock/gtExtras/man/gt_hyperlink.html")
  # web_image(
  #       url = svg_badge,
  #       height = px(100)
  #     )
# gt_hyperlink
```


# Code

The code of this Shiny app is open and freely available on a [GitHub repository](https://github.com/firms-gta/shiny_compare_fisheries_datasets) and main releases have been assigned DOIs on Zenodo. The code can be directly executed within the RStudio server hosted by the virtual lab. 

# IRD Tuna Atlas legacy

Part of this work is inherited from previous IRD "[Atlas of tropical tuna fisheries - World catches and environment](https://horizon.documentation.ird.fr/exl-doc/pleins_textes/divers11-03/010012425.pdf)" written by Alain Fonteneau and Sardara project.

[<img src="Atlas_Alain_FontenauFront_Page.svg" height="100px">](https://www.documentation.ird.fr/hor/fdi:010012425).


# Contact

This collaborative work has been achieved by IRD (Shiny app code) with the support of CNR in the context of the Blue-Cloud 2026 EU reserch project.
If needed please contact Julien Barde [<img src="logo_ORCID.svg" height="10%">](https://orcid.org/0000-0002-3519-6141) or 
Bastien Grasset [<img src="logo_ORCID.svg" height="10%">](https://orcid.org/0000-0002-9946-1338)
# General Disclaimer

This repository contains work in progress. Results presented here do not represent the official view of IRD, its staff or consultants. Caution must be taken when interpreting all data presented, and differences between information products published by IRD and other sources using different inclusion criteria and different data cut-off times are to be expected. While steps are taken to ensure accuracy and reliability, all data are subject to continuous verification and change. See here for further background and other important considerations surrounding the source data.


**References**

```{r results = "asis", echo = FALSE}
NoCite(biblio, title = "*")
PrintBibliography(biblio, .opts = list(check.entries = FALSE))
```

[<img src="logo_blue-cloud_2026.svg" height="10%">](https://blue-cloud.d4science.org)

# Funding
This work has received funding from the European Union’s Horizon Europe research and innovation programme under grant agreement No. [101094227](https://doi.org/10.3030/101094227) and No. [862409](https://doi.org/10.3030/862409) (Blue-Cloud H2020 project).

</div>